---
title: "R Notebook"
author: "Meghan Moody"
output: html_notebook
---

# R as a Programming Language 

## Data Types: 

### Vectors 
- you can not mix and match data types in vectors
```{r}
a <- c(1,2,3)
a1 <- c(1.0, 2.0, 3.0)
b <- c("a", "b", "c")
c <- c(TRUE, FALSE, TRUE)
d <- c(1, "a", TRUE)
class(a)
class(a1)
class(b)
class(c)
class(d)
d

x <- 2
as.character(x)

f <- as.factor(c())

```
```{r}
a <- c('a', 'b', 'c')
a[1:2]
length(a)
for (i in 1:length(a)){
  cat(paste(a[i], "\n"))
}
a[1] <- "z"
a
```
###Lists 
- can have a mixmatch of data types and can have nexted list 
```{r}
l <- list()
l[[1]] <- 1
l[[2]] <- 2 
l[[3]] <- "a"
l
```
- hash structure of list 
```{r}
l1 <- list(a="First", b=2, c=TRUE)
l1[[1]]
l1[['a']]
```
- NA has a specific meaning that there is nothing there like NULL

```{r}
na_v <- c(1,2,NA,3)
```

##Data Structures:
###Data Frames

-like a table with columns and rows 
-str gives an broad overview of what the data looks like
```{r}
data(iris)
str(iris)
View(iris)
dim(iris)
dim(iris)[1]
head(iris)
table(iris)
iris[,1]
names(iris)
iris$Sepal.Length
names(iris) <- c("a", "b", "c", "d", "e")
names(iris)
iris$a
data("iris")
table(iris$Species)
summary(iris)
```
### CVS and TSV files

-save the sample iris data to my directory called my_iris
```{r}
write.table(iris, file = "my_iris.tsv", quote = F, row.names = F, sep = "\t")

```

```{r}
my_iris <- read.table("my_iris.tsv")
names(my_iris) <- my_iris[1, ]
my_iris <- my_iris[-1, ]
View(my_iris)
```
- The above black can be simplied down to 
```{r}
my_iris <- read.table("my_iris.tsv")
View(my_iris)
```

## Ploting in R 

-the most common ploting function in base R is plot 

```{r}
plot(my_iris$Sepal.Length, my_iris$Sepal.Width, xlab = "Sepal Length", ylab = "Sepal Width", main = "My Great Plot")
```

- ggplot is the popular version to use now 
```{r}
library(ggplot2)
ggplot(my_iris, aes(x=Sepal.Length, y=Sepal.Width)) + geom_point() + xlab("Sepal Length") + ylab("Sepal Width")
```

