---
title: "INFO302_classnotes"
author: "Meghan Moody"
date: "9/14/2021"
output: html_notebook
---
# R Enviorment 

- ctrl+alt+i inserts an R code block 

- if you want to write in another language in the curly bracket  do {r engine= "selected language"}

- everything is a function in R
```{r}
getwd()
setwd("/home/mmeghan")
getwd()

a <- 2
testfunction <- function() {
  x <- rnorm(100)
  mean(x)
}
testfunction()

```

# Getting Help

- in Unix there is a command called man 

- for R you add a question mark to the funciton 
```{r}
?getwd()

```
- CRAN website has tutorals for the packages 

- Biocondunctor has bunch of information on how to install packages and how they work

- Package Vignettes are tutorials 


#Install Packages 

- The install.packages() only installs packages from CRAN

- With the install of Bio C Manager, packages from Bioconductor can be downloaded on command 

- R packages can also download data 

```{r}
install.packages("BiocManager")

```
- once a package is installed there are two ways to use the package 
- In R to call a function from a specific package is called "namespace"
- Like in java to call a function of an object you would do Object.function()
-For R to call a function from a specified package there are two ways
  

```{r}
#Method 1
library(BiocManager)
install()
#Method 2 
#Going forward use this method
BiocManager::install("ggplot2")
library(ggplot2)
```

- By default packages are dowloaded in ~/R



