---
title: "Ploting in R"
author: "Meghan Moody"
date: "September 28, 2021 "
output: html_notebook
---

# Ploting in R 

-the most common ploting function in base R is plot 

```{r}
names(my_iris)
plot(my_iris$Sepal.Length, my_iris$Sepal.Width, xlab = "Sepal Length", ylab = "Sepal Width", main = "My Great Plot")
```

- ggplot is the popular version to use now 

```{r}
library(ggplot2)
ggplot(my_iris, aes(x=Sepal.Length, y=Sepal.Width)) + geom_point() + xlab("Sepal Length") + ylab("Sepal Width")
```
## Histograms


```{r}
data <- runif(1000)
hist(data)
hist(data+data+data+data+data+data)

```

- Calculating Z scores 

```{r}
mean(data)
sd(data)
(2-mean(data))/sd(data)
```

## Box Plot 

```{r}
boxplot(airquality)
g <- ggplot(airquality, aes(x=as.factor(Month), y=Ozone))+geom_boxplot()
g

```


```{r}
library(tidyr)
gather_data <- gather(airquality)
g <- ggplot(gather_data, aes(x=key, y=value)) + geom_boxplot()
g
```
## Linear Regression and Correlation


- Create a random distribution with mean 2 and standard devation of 1 for thought experiment that a man catches a fish everyday for a year and on avgerage catches a fish between 1 and 3 feet. What is the probability of catching a fish that is 5 feet long 

```{r}
fish_data <- rnorm(n=365, mean=2, sd =1)
hist(fish_data)

z_score <- (5-mean(fish_data))/sd(fish_data)
z_score


probability <- 1- pnorm(z_score)
probability

```

## Data Minning

- you give a set of data and then create a model of that data and then given a particualr point what would be the features of that particular point 

- Linear Regression is a function in the form y=mx+b and fits a linar line though the data with the same amout of data points above and below the line 

- Gradient Descent

